Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-05 WRITEUP/ms.tex
refine abstract again

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) in a prototypical galaxy (\flower)
and its satellite galaxies at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
We identify MCs using H$_2$ density, 
and compare their masses, sizes, velocity dispersions, gas surface densities, and virial parameters ($\alpha_{\rm vir}$)
with those observed in nearby and \z$\sim$\,2 galaxies.
The MCs span a mass range of $10^{6.5-9}$\,\Msun. Their velocity dispersions and gas surface densities are 
systematically higher than those observed in nearby galaxies but comparable to 
starburst galaxies, with $\sigma\gtrsim$\,100\,\kms.
% Toomre Q
We compute the effective two-component Toomre Q parameter (gas and stars) to examine 
regions that are unstable to local axisymmetric perturbations. 
We further perform virial analysis, which is observable, to examine collapsing regions.
Virial analysis indicates that the MCs in the main disk of \flower are unbound, but its 
substructures have lower virial parameters,
consistent with the notion that collapsing structures result from gravitational instability within globally stable structures.
% , which are supported by turbulence and rotation on large scale.
We find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, 
which we interpret as result from the weaker stellar feedback
due to the less frequent \SF compared to \flower.
Our results suggest that the more massive and bigger MCs of \flower compared to the Milky Way
manifest from the higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the
Next Generation Very Large Array (ngVLA)
will furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

>>>>

\begin{abstract}
We study the dynamical properties of molecular clouds complexes (MC) in a prototypical galaxy (\flower)
and its satellite galaxies at the Epoch of Reionization (EoR) using cosmological zoom-in simulation.
We identify MCs using H$_2$ density, 
and compare their masses, sizes, velocity dispersions, gas surface densities, and virial parameters ($\alpha_{\rm vir}$)
with those observed in nearby and \z$\sim$\,2 galaxies.
The MCs span a mass range of $10^{6.5-9}$\,\Msun. Their velocity dispersions and gas surface densities are 
systematically higher than those observed in nearby galaxies, but comparable to starburst galaxies.
We compute the effective two-component Toomre Q parameter (gas and stars) to examine 
regions that are unstable to local axisymmetric perturbations. 
We further perform virial analysis, which is accessible from observations, to examine regions likely to be undergo collapse.
Our analysis indicates that the MCs in the main disk of \flower are unbound, but its 
substructures have lower virial parameters, which is
consistent with the notion that collapsing structures result from gravitational instability within globally stable structures.
% , which are supported by turbulence and rotation on large scale.
On the other hand, we find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies,
which we interpret as result of the weaker stellar feedback and less frequent \SF compared to \flower.
Our results suggest that the more massive and bigger MCs compared to the Milky Way
manifest from the higher gas mass fraction, surface density, and velocity dispersion.
% , which together sets the scale for fragmentation.
High resolution imaging of the first galaxies with the Atacama Large (sub-)Millimeter Array (ALMA) and the
Next Generation Very Large Array (ngVLA)
can furnish scrutinizing data to test our findings and shed light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}
